Formal Synthesis of Digital Controllers for Observable Continuous Plants with Transient Performance Specifications

### 2018-04-17 CAV2018/paper.tex
paragraph -> subsection

\paragraph{\underline{{\sc abstract}}} computes an initial version of $\phi$

@@

\paragraph{\underline{{\sc synthesize}}} generates a candidate controller matrix $\mat{K}_{\langle P \rangle}$

@@

\paragraph{\underline{{\sc Verify}}} checks whether the candidate

@@

\paragraph{\underline{{\sc Refine Abstraction and optimize}}} refines the
model abstraction as well as optimizes the current candidate
solution.
%
First, the model abstraction must be refined in order to eliminate
the newly received counterexample. For this purpose,
we increase the time horizon $n$ for the
safety specification so that it captures the violating iteration
(for the given initial state) and adjust $\phi$ as 
$\phi := \phi \wedge \phi_\mathit{safety}^n$.
If~the counterexample is provided by the {\sc continuous time} stage,
then we must select a smaller suitable sample time to be used
for the model discretization.
%% and modify the abstractions to meet the discretization 
%% ($\phi_{synth} = \phi_{synth} \wedge \phi_{sample}^{T_d'}$ and $\phi_{static} = \phi_{static} \wedge \phi_{sample}^{T_d'}$).
%% It will then feed back to the abstraction refinement loop to look for a suitable action for the updated model.
%\end{enumerate}

>>>>

\subsection*{\underline{{\sc abstract}}} computes an initial version of $\phi$

@@

\subsection*{\underline{{\sc synthesize}}} generates a candidate controller matrix $\mat{K}_{\langle P \rangle}$

@@

\subsection*{\underline{{\sc Verify}}} checks whether the candidate

@@

\subsection*{\underline{{\sc Refine Abstraction and optimize}}} refines the
model abstraction as well as optimizes the current candidate
solution.
%
First, the model abstraction must be refined in order to eliminate
the newly received counterexample. For this purpose,
we increase the time horizon $n$ for the
safety specification so that it captures the violating iteration
(for the given initial state) and adjust $\phi$ as 
$\phi := \phi \wedge \phi_\mathit{safety}^n$.
If~the counterexample is provided by the {\sc continuous time} stage,
then we must select a smaller suitable sample time to be used
for the model discretization.
%% and modify the abstractions to meet the discretization 
%% ($\phi_{synth} = \phi_{synth} \wedge \phi_{sample}^{T_d'}$ and $\phi_{static} = \phi_{static} \wedge \phi_{sample}^{T_d'}$).
%% It will then feed back to the abstraction refinement loop to look for a suitable action for the updated model.
%\end{enumerate}
